---
title: "ps2-feedback"
format: html
editor: visual
---

## PS2 feedback

I'd like to see you work to provide commentary on the output of your code chunks. For instance, what do you learn when you run `str()` and `glimpse()`? What does that code tell you about your data? You should be writing it down.

At line 43, you should also run `levels()` after running `factor()` to see what the new levels of your factor are. Same for line 57.

On line 74, why did you group by costume? That step was not necessary.

In figure 2, you didn't adjust your axis labels.

Lines 85 - 89, you can work to make your code more readable using spacing. Here's what you have:

```{r}
hallow|>
  group_by(sugar_high)|>
  summarise(mean(age),mean(g_candy_consumed),sd(age), sd(g_candy_consumed))|>
  View()
```

Here is exactly the same code, but easier to read:

```{r}
hallow|>
  group_by(sugar_high)|>
  summarise(
    mean(age),
    mean(g_candy_consumed),
    sd(age), 
    sd(g_candy_consumed))|>
  View()
```
Notice that because you did not name new variables in your summarise() statement, the tabular view has weird column names.

You could have done:
```{r}
hallow|>
  group_by(sugar_high)|>
  summarise(
    mean_age = mean(age),
    mean_g_candy = mean(g_candy_consumed),
    sd_age = sd(age), 
    sd_g_candy = sd(g_candy_consumed))|>
  View()
```

For figure 3, notice that I have different levels for my factors than you do.
